A Comparison of Graph Processing Systems

### 2020-09-03 documentation/paper/main.tex
giraph overview is less ugly now

@@

% Generated by IEEEtran.bst, version: 1.12 (2007/01/11)
\begin{thebibliography}{1}
\providecommand{\url}[1]{#1}
\csname url@samestyle\endcsname
\providecommand{\newblock}{\relax}
\providecommand{\bibinfo}[2]{#2}
\providecommand{\BIBentrySTDinterwordspacing}{\spaceskip=0pt\relax}
\providecommand{\BIBentryALTinterwordstretchfactor}{4}
\providecommand{\BIBentryALTinterwordspacing}{\spaceskip=\fontdimen2\font plus
\BIBentryALTinterwordstretchfactor\fontdimen3\font minus
  \fontdimen4\font\relax}
\providecommand{\BIBforeignlanguage}[2]{{%
\expandafter\ifx\csname l@#1\endcsname\relax
\typeout{** WARNING: IEEEtran.bst: No hyphenation pattern has been}%
\typeout{** loaded for the language `#1'. Using the pattern for}%
\typeout{** the default language instead.}%
\else
\language=\csname l@#1\endcsname
\fi
#2}}
\providecommand{\BIBdecl}{\relax}
\BIBdecl

@@

>>>>

\input{sections/relatedWork}

@@

% Generated by IEEEtran.bst, version: 1.12 (2007/01/11)
\begin{thebibliography}{10}
\providecommand{\url}[1]{#1}
\csname url@samestyle\endcsname
\providecommand{\newblock}{\relax}
\providecommand{\bibinfo}[2]{#2}
\providecommand{\BIBentrySTDinterwordspacing}{\spaceskip=0pt\relax}
\providecommand{\BIBentryALTinterwordstretchfactor}{4}
\providecommand{\BIBentryALTinterwordspacing}{\spaceskip=\fontdimen2\font plus
\BIBentryALTinterwordstretchfactor\fontdimen3\font minus
  \fontdimen4\font\relax}
\providecommand{\BIBforeignlanguage}[2]{{%
\expandafter\ifx\csname l@#1\endcsname\relax
\typeout{** WARNING: IEEEtran.bst: No hyphenation pattern has been}%
\typeout{** loaded for the language `#1'. Using the pattern for}%
\typeout{** the default language instead.}%
\else
\language=\csname l@#1\endcsname
\fi
#2}}
\providecommand{\BIBdecl}{\relax}
\BIBdecl

@@

\bibitem{pregel}
\BIBentryALTinterwordspacing
G.~Malewicz, M.~H. Austern, A.~J. Bik, J.~C. Dehnert, I.~Horn, N.~Leiser, and
  G.~Czajkowski, ``Pregel: A system for large-scale graph processing,'' in
  \emph{Proceedings of the 2010 ACM SIGMOD International Conference on
  Management of Data}, ser. SIGMOD '10.\hskip 1em plus 0.5em minus 0.4em\relax
  New York, NY, USA: Association for Computing Machinery, 2010, p. 135–146.
  [Online]. Available: \url{https://doi.org/10.1145/1807167.1807184}
\BIBentrySTDinterwordspacing

\bibitem{mapreduce}
J.~Dean and S.~Ghemawat, ``Mapreduce: Simplified data processing on large
  clusters,'' in \emph{In Proceedings of Operating Systems Design and
  Implementation (OSDI}, pp. 137--150.

### 2020-09-03 documentation/paper/sections/overview/giraph.tex
giraph overview is less ugly now

Apache Giraph is an iterative graph processing framework, built on top of Apache Hadoop \cite{Giraph}. Hadoop is a large MapReduce infrastructure providing a reliable (fault tolerant) basis for large scale graph processing.

Giraph is an example for an open-source system similar to Pregel.
Thus, Giraph's computation model is closely related to the BSP model discussed in \autoref{sec:bsp}. 
//TODO: Hier wiederholt sich jetzt einiges.. ärgerlich.

// Mapreduce: Giraph uses the Map functionality of Hadoop to run the algorithms, Reduce is only used as an identity function.

This means that Giraph is based on computation units that communicate using messages and are synchonized with barriers.

@@

Computation is vertex oriented and iterative.
For each iteration step called superstep, the Compute method implementing the algorithm is invoked on each active vertex, with every vertex being active in the beginning.
This method receives messages sent in the previous superstep as well as its vertex value and the values of outgoing edges.
With this data the values are modified and messages to other vertices are sent.
Communication between vertices is only performed via messages, so a vertex has no access to values of other vertices or edges other than its own outgoing ones.

Supersteps are synchronized with barriers, meaning that all messages only get delivered in the following superstep and computation for the next superstep can only begin after every vertex has finished computing the current superstep.
Edge and vertex values are retained across supersteps.

Any vertex can stop computing (i.e. setting its state to inactive) at any time but incoming messages will reactivate the vertex again.
A vote-to-halt method is applied, i.e. if all vertices are inactive or if a user defined superstep is reached the computation ends.
Once calculation is finished, each vertex outputs some local information (e.g. the final vertex value) as result.

Because of the underlying Hadoop infrastructure, expanding single-node processing to a multi-node cluster is seamless. Hadoop supplies a distributed file system (HDFS), on which all computation is performed. Giraph is thus, even when only using a single node, running in a distributed manner.

@@

TODO: Facebook?

>>>>

Apache Giraph is an example for an open-source system similar to Pregel.
Thus, Giraph's computation model is closely related to the BSP model discussed in \autoref{sec:bsp}. 
This means that Giraph is based on computation units that communicate using messages and are synchonized with barriers \cite{Giraph}.

@@

Computation is vertex oriented and iterative.
For each iteration step called superstep, the Compute method implementing the algorithm is invoked on each active vertex, with every vertex being active in the beginning.
This method receives messages sent in the previous superstep as well as its vertex value and the values of outgoing edges.
With this data the values are modified and messages to other vertices are sent.
Communication between vertices is only performed via messages, so a vertex has no access to values of other vertices or edges other than its own outgoing ones.
Supersteps are synchronized with barriers, meaning that all messages only get delivered in the following superstep and computation for the next superstep can only begin after every vertex has finished computing the current superstep.
Edge and vertex values are retained across supersteps.
Any vertex can stop computing (i.e. setting its state to inactive) at any time but incoming messages will reactivate the vertex again.
A vote-to-halt method is applied, i.e. if all vertices are inactive or if a user defined superstep is reached the computation ends.
Once calculation is finished, each vertex outputs some local information (e.g. the final vertex value) as result.

In order for Giraph a achieve scalability and parallelization, it is built on top of Apache Hadoop \cite{Giraph}.
Hadoop is a MapReduce infrastructure providing a fault tolerant basis for large scale graph processing.
Hadoop supplies a distributed file system (HDFS), on which all computation is performed.
Giraph is thus, even when only using a single node, running in a distributed manner.
But expanding single-node processing to a multi-node cluster is seamless.
Giraph uses the Map functionality of Hadoop to run the algorithms, Reduce is only used as the identity function.

@@
